---
title: "Figure3 - old Fig 5"
author: "Athena Golfinos-Owens" - "Huy Dinh editted 2025-09-25"
date: "2025-01-15"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(Seurat)
library(dplyr)
library(tidyr)
library(readxl)
library(CellChat)
library(DescTools)
library(circlize)
library(openxlsx)
library(ComplexHeatmap)
library(ggplot2)
library(ggrepel)
library(grid)
library(future)

```{r Fig 3A--Running per Neighborhood CellChat for heatmap}
library(Seurat)
library(CellChat)
library(patchwork)
library(future)

## Object load-in
```{r}
# loading in necessary objects
```

setwd(dirname(rstudioapi::getActiveDocumentContext()$path)) 
print(getwd())

CosMX_RNA_merged$k10_NhCoord20_anno[CosMX_RNA_merged$k10_NhCoord20_anno == "Myeloid_K17+_Tumor_Mixed"] <- 'Myeloid_K17_Tumor_Mixed'

# Get unique entries from k10_NhCoord20_anno
unique_entries <- unique(CosMX_RNA_merged$k10_NhCoord20_anno)

# Define the analysis function
run_analysis <- function(entry) {
  cosmx_rna_nh <- CosMX_RNA_merged[,grep(entry, CosMX_RNA_merged$k10_NhCoord20_anno)]
  
  data.input1 = Seurat::GetAssayData(cosmx_rna_nh[,cosmx_rna_nh$Response == 'R'], slot = "data", assay = "SCT")
  data.input2 = Seurat::GetAssayData(cosmx_rna_nh[,cosmx_rna_nh$Response == 'NR'], slot = "data", assay = "SCT")
  
  genes.common <- intersect(rownames(data.input1), rownames(data.input2))
  colnames(data.input1) <- paste0("R_", colnames(data.input1))
  colnames(data.input2) <- paste0("NR_", colnames(data.input2))
  
  meta1 = data.frame(labels = cosmx_rna_nh[,cosmx_rna_nh$Response == 'R']$annot_cluster2, samples = cosmx_rna_nh[,cosmx_rna_nh$Response == 'R']$tma_fov_id)
  meta2 = data.frame(labels = cosmx_rna_nh[,cosmx_rna_nh$Response == 'NR']$annot_cluster2, samples = cosmx_rna_nh[,cosmx_rna_nh$Response == 'NR']$tma_fov_id)
  
  rownames(meta1) <- colnames(data.input1)
  rownames(meta2) <- colnames(data.input2)
  meta1$labels <- factor(meta1$labels, levels = unique(meta1$labels))
  meta1$samples <- factor(meta1$samples, levels = unique(meta1$samples))
  meta2$labels <- factor(meta2$labels, levels = unique(meta2$labels))
  meta2$samples <- factor(meta2$samples, levels = unique(meta2$samples))
  
  r_cellchat <- createCellChat(object = data.input1, meta = meta1, group.by = "labels", datatype = "RNA")
  nr_cellchat <- createCellChat(object = data.input2, meta = meta2, group.by = "labels", datatype = "RNA")
  
  CellChatDB <- CellChatDB.human 
  CellChatDB.use <- subsetDB(CellChatDB)
  
  r_cellchat@DB <- CellChatDB.use
  nr_cellchat@DB <- CellChatDB.use
  
  r_cellchat <- subsetData(r_cellchat)
  future::plan("multisession", workers = 4) 
  r_cellchat <- identifyOverExpressedGenes(r_cellchat)
  r_cellchat <- identifyOverExpressedInteractions(r_cellchat)
  r_cellchat <- computeCommunProb(r_cellchat, type = "truncatedMean", trim = 0.1, distance.use = F)
  r_cellchat <- filterCommunication(r_cellchat, min.cells = 10)
  r_cellchat <- computeCommunProbPathway(r_cellchat)
  r_cellchat <- aggregateNet(r_cellchat)
  
  nr_cellchat <- subsetData(nr_cellchat)
  future::plan("multisession", workers = 4) 
  nr_cellchat <- identifyOverExpressedGenes(nr_cellchat)
  nr_cellchat <- identifyOverExpressedInteractions(nr_cellchat)
  nr_cellchat <- computeCommunProb(nr_cellchat, type = "truncatedMean", trim = 0.1, distance.use = F)
  nr_cellchat <- filterCommunication(nr_cellchat, min.cells = 10)
  nr_cellchat <- computeCommunProbPathway(nr_cellchat)
  nr_cellchat <- aggregateNet(nr_cellchat)
  
  all_levels <- unique(c(levels(r_cellchat@idents), levels(nr_cellchat@idents)))
  cell_order1 <- levels(r_cellchat@idents) 
  cell_order2 <- levels(nr_cellchat@idents)
  cell_order <- intersect(cell_order1, cell_order2)
  
  r_cellchat <- CellChat::updateClusterLabels(r_cellchat, new.order = cell_order) %seed% TRUE
  nr_cellchat <- CellChat::updateClusterLabels(nr_cellchat, new.order = cell_order) %seed% TRUE
  
  pathways.show <- c("CXCL") 
  
  color_clusters <- c("#DC050C", "#FB8072", "#1965B0", "#7BAFDE", "#882E72", "#B17BA6", "#FF7F00", "#FDB462",
                      "#E7298A", "#E78AC3","#33A02C", "#B2DF8A", "#55A1B1", "#8DD3C7", "#A6761D", "#E6AB02", 
                      "#7570B3", "#BEAED4", "#666666", "#999999", "#AA8282", "#D4B7B7", "#8600BF", "#BA5CE3", 
                      "#808000","#AEAE5C", "#1E90FF", "#00BFFF", "#56FF0D", "#FFFF00")
  
  p1 <- netVisual_aggregate(nr_cellchat, signaling = pathways.show, layout = "circle", 
                            sources.use = grep('Mon|Mac|DC', meta1$labels, value = T), 
                            targets.use = grep('Tcells|CD8|CD4|Treg', meta1$labels, value = T), remove.isolate = T)
  pdf(paste0(entry, '_NR_circos.pdf'), width = 6, height = 6)
  print(p1)
  dev.off() 
  
  p2 <- netVisual_aggregate(r_cellchat, signaling = pathways.show, layout = "circle", 
                            sources.use = grep('Mon|Mac|DC', meta1$labels, value = T), 
                            targets.use = grep('Tcells|CD8|CD4|Treg', meta1$labels, value = T), remove.isolate = T)
  pdf(paste0(entry, '_R_circos.pdf'), width = 6, height = 6)
  print(p2)
  dev.off()
  
  pdf(paste0(entry, '_myeloid_to_tcell_chord_diagram_NR_R.pdf'), pointsize = 12, height = 6, width = 9)
  print(cowplot::plot_grid(p2, p1, ncol = 2))
  dev.off()
  
  r <- subsetCommunication(r_cellchat, sources.use = grep('Mon|Mac|DC', meta1$labels, value = T), targets.use = grep('Tcells|CD8|CD4|Treg', meta1$labels, value = T))
  nr <- subsetCommunication(nr_cellchat, sources.use = grep('Mon|Mac|DC', meta2$labels, value = T), targets.use = grep('Tcells|CD8|CD4|Treg', meta2$labels, value = T))
  
  r_cxcl <- subsetCommunication(r_cellchat, sources.use = grep('Mon|Mac|DC', meta1$labels, value = T), targets.use = grep('Tcells|CD8|CD4|Treg', meta1$labels, value = T), signaling = 'CXCL')
  nr_cxcl <- subsetCommunication(nr_cellchat, sources.use = grep('Mon|Mac|DC', meta2$labels, value = T), targets.use = grep('Tcells|CD8|CD4|Treg', meta2$labels, value = T), signaling = 'CXCL')
  
  save(r_cellchat, nr_cellchat, CellChatDB, CellChatDB.use, cosmx_rna_nh, data.input1, data.input2, meta1, meta2,
       file = paste0(entry, '_workspace.rda'))
  
  cellchat <- mergeCellChat(list(r_cellchat, nr_cellchat), add.names = c('Responder', 'Non-Responder'))
  
  gg1 <- rankNet(cellchat, mode = "comparison", measure = "weight", sources.use = grep('Mon|Mac|DC', meta1$labels, value = T), 
                 targets.use = grep('Treg|CD4|CD8', meta1$labels, value = T), stacked = T, do.stat = TRUE, return.data = T)
  gg2 <- rankNet(cellchat, mode = "comparison", measure = "weight", sources.use = grep('Mon|Mac|DC', meta1$labels, value = T), 
                 targets.use = grep('Treg|CD4|CD8', meta1$labels, value = T), stacked = F, do.stat = TRUE, return.data = T)
  
  stacked_df <- gg1$signaling.contribution
  unstacked_df <- gg2$signaling.contribution
  
  # Save additional results if needed
  save(stacked_df, unstacked_df, file = paste0(entry, '_additional_results.rda'))
}

# Loop through unique entries and run the analysis
for (entry in unique_entries) {
  tryCatch({
    cat("Processing entry:", entry, "\n")
    run_analysis(entry)
    cat("Completed processing for entry:", entry, "\n\n")
  }, error = function(e) {
    cat("Error processing entry:", entry, "\n")
    cat("Error message:", conditionMessage(e), "\n\n")
  })
}

```

```{r Fig 4c--only myeloid senders!preparing pathway by probability dataframe for heatmap and plotting}
library(dplyr)
library(purrr)
library(readr)
library(CellChat)
library(stringr)
library(tidyr)
library(ComplexHeatmap)
library(circlize)
library(RColorBrewer)
library(ggraph)

# Define file paths
files <- c(
  'Tumor_Immune_Mixed_workspace.rda',
  'Myeloid_K17_Tumor_Mixed_workspace.rda',
  'Macrophage_High_workspace.rda',
  'DC_T_iCAF_Tumor_Mixed_workspace.rda',
  'CAF_Immune_Mixed_workspace.rda'
)

# Set working directory
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
print(getwd())

# Function to load workspace and extract CellChat objects
load_cellchat_objects <- function(file_path) {
  load(file_path)
  
  # Check if objects exist
  if (!exists("nr_cellchat") || !exists("r_cellchat")) {
    stop(paste("Missing nr_cellchat or r_cellchat in", file_path))
  }
  
  list(
    nr = nr_cellchat,
    r = r_cellchat
  )
}

# Function to extract the name
extract_name <- function(file_path) {
  file_name <- basename(file_path) # Gets filename
  name <- gsub("_workspace\\.rda$", "", file_name)  # Removes suffix
  return(name)
}

# Apply the function to all files and store in a list
cellchat_list <- map(files, load_cellchat_objects)

# Extract the names for the list
names(cellchat_list) <- map_chr(files, extract_name)

# Print the structure of the resulting list
str(cellchat_list, max.level = 2)

# Initialize list to store merged CellChat objects
merged_cellchat_list <- list()

# Merge CellChat objects for each neighborhood
for (neighborhood in names(cellchat_list)) {
  # Merge nr and r CellChat objects
  nr <- cellchat_list[[neighborhood]]$nr
  r <- cellchat_list[[neighborhood]]$r
  
  # Perform the merging
  merged_cellchat <- tryCatch({
    mergeCellChat(list(R = r, NR = nr), add.names = c("R", "NR"))
  }, error = function(e) {
    message(sprintf("Error merging %s: %s", neighborhood, e$message))
    return(NULL)
  })
  
  # Check the results
  if (!is.null(merged_cellchat)) {
    merged_cellchat_list[[neighborhood]] <- merged_cellchat
  }
}

# Filter out NULL entries (failed merges)
merged_cellchat_list <- merged_cellchat_list[!sapply(merged_cellchat_list, is.null)]

# Get all unique pathways from merged objects
all_pathways <- unique(merged_cellchat_list[[1]]@netP$R$pathways)

# Initialize list to store results
results_list <- list()

# Loop through merged CellChat objects and pathways
for (neighborhood in names(merged_cellchat_list)) {
  merged_cellchat_obj <- merged_cellchat_list[[neighborhood]]
  
  # Initialize list for this neighborhood's results
  neighborhood_results <- list()
  
  # Loop through pathways
  for (pathway in all_pathways) {
    tryCatch({
      # Run netVisual_bubble and extract data
      plot_data <- netVisual_bubble(
        merged_cellchat_obj,
        signaling = pathway,
        sources.use = c('Macrophages', 'Monocytes', 'DCs'),
        targets.use = c('TcellsCD8+', 'Tcells_CD4+', 'Tregs'),
        remove.isolate = FALSE,
        return.data = TRUE,
        comparison = c(1, 2)
      )
      
      # Add pathway and neighborhood information
      result_df <- plot_data$communication %>%
        mutate(
          pathway = pathway,
          neighborhood = neighborhood
        )
      
      # Store results
      neighborhood_results[[pathway]] <- result_df
    }, error = function(e) {
      message(sprintf("Error processing pathway %s in %s: %s",
                      pathway, neighborhood, e$message))
    })
  }
  
  # Combine results for this neighborhood
  if (length(neighborhood_results) > 0) {
    combined_results <- bind_rows(neighborhood_results)
    results_list[[neighborhood]] <- combined_results
  }
}

# Combine all results into a single dataframe
final_results <- bind_rows(results_list)

# Print the structure of the final results
str(final_results)

final_results <- final_results %>%
  mutate(
    neighborhood = case_when(
      neighborhood == "Tumor_Immune_Mixed" ~ 'Tumor_Immune_Tcell_High',
      neighborhood == "Macrophage_High" ~ "Immune_Macrophage_High",
      neighborhood == "DC_T_iCAF_Tumor_Mixed" ~ "ap_iCAF_Immune_Mixed",
      neighborhood == "CAF_Immune_Mixed" ~ "myCAF_Immune_Mixed",
      TRUE ~ as.character(neighborhood)
    )
  )


# Save the results
write.csv(final_results, "cellchat_netVisual_bubble_merged_results.csv", row.names = FALSE)

combined_df <- read.csv("cellchat_netVisual_bubble_merged_results.csv")

combined_df <- combined_df[!combined_df$pathway %in% c("MHC-I", 'MHC-II', 'COLLAGEN'),]

library(dplyr)

combined_df <- combined_df[!is.na(combined_df$prob),]

combined_df <- combined_df %>%
  group_by(neighborhood) %>%
  mutate(
    prob.original_rescaled = (prob.original - min(prob.original)) / (max(prob.original) - min(prob.original)),
    prob_rescaled = (prob - min(prob)) / (max(prob) - min(prob))
  ) %>%
  ungroup()



# Sanity checks
sanity_check <- combined_df %>%
  group_by(neighborhood) %>%
  summarise(
    min_prob_original = min(prob.original_rescaled),
    max_prob_original = max(prob.original_rescaled),
    min_prob = min(prob_rescaled),
    max_prob = max(prob_rescaled)
  )

print(sanity_check)

# Additional check for any NA values
na_check <- combined_df %>%
  summarise(
    na_prob_original = sum(is.na(prob.original_rescaled)),
    na_prob = sum(is.na(prob_rescaled))
  )

print(na_check)






combined_df <- combined_df %>% 
  select('source.target', 'interaction_name', 'neighborhood', 'prob_rescaled', 'pathway')
combined_df$id <- paste(combined_df$source.target, combined_df$neighborhood)
combined_df$id2 <- paste(combined_df$interaction_name, combined_df$pathway)

#additional filter
tmp <- combined_df
#count_pathway <- plyr::count(combined_df$pathway)
#combined_df <- combined_df[-which(combined_df$pathway %in% count_pathway$x[which(count_pathway$freq<3)]),]
#combined_df <- combined_df[which(combined_df$pathway %in% c("IL1", "IL4", "IL16", "IL6")),]
#combined_df <- tmp[which(tmp$pathway %in% c("CD40", "CD86", "CD80")),]
combined_df <- tmp[which(tmp$pathway %in% c("CXCL", "CCL", "IL1", "IL16", "IL4", "IL6")),]


anno_df_col <- combined_df 
anno_df_row <- combined_df
library(stringr)

anno_df_col$Response <- str_extract(anno_df_col$source.target, "\\(([^)]+)\\)")
anno_df_col$Response <- str_remove_all(anno_df_col$Response, "[()]")
anno_df_col <- anno_df_col %>%
  select('Response', 'id', 'neighborhood')
anno_df_col <- unique(anno_df_col)
library(tidyr)
anno_df_col <- anno_df_col[!is.na(anno_df_col$Response),]

anno_df_col <- anno_df_col %>%
  separate("id", into = c("sender", "temp"), sep = "->", remove = FALSE) %>%
  separate("temp", into = c("receiver", "response"), sep = "\\(", remove = TRUE)


combined_df_wide <- combined_df %>% 
  select('id', 'id2', 'prob_rescaled')
combined_df_wide <- unique(combined_df_wide)
combined_df_wide <- tidyr::pivot_wider(combined_df_wide, names_from = id, values_from = prob_rescaled)

combined_df_wide <- as.data.frame(combined_df_wide[!is.na(combined_df_wide$id2),])
combined_df_wide[is.na(combined_df_wide)] <- 0
combined_df_wide <- combined_df_wide[grep('NA ', combined_df_wide$id, invert = T),]
rownames(combined_df_wide) <- combined_df_wide$id2
combined_df_wide$id2 <- NULL

# Define a vector of distinct colors for your neighborhoods
neighborhood_colors <- c(
  "Tumor_Immune_Tcell_High" = "#E41A1C",
  "Immune_Macrophage_High" = "#377EB8",
  "Myeloid_K17_Tumor_Mixed" = "#4DAF4A",
  "ap_iCAF_Immune_Mixed" = "#984EA3",
  "myCAF_Immune_Mixed" = "#FF7F00"
)

response_colors <- c(
  'R' = '#FF8A80',
  'NR' = '#2196F3'
)

sender_colors <- c(
  "Monocytes " = 'green',
  "Macrophages " = 'green4',
  "DCs " = 'navy'
)

receiver_colors <- c(
  ' TcellsCD8+ ' = 'yellow',
  ' Tcells_CD4+ ' = 'skyblue',
  ' Tregs ' = 'orange'
)

# Create the column annotation
col_anno <- ComplexHeatmap::HeatmapAnnotation(
  Response = anno_df_col$Response,
  Neighborhood = anno_df_col$neighborhood,
  Sender = anno_df_col$sender,
  Receiver = anno_df_col$receiver,
  col = list(Neighborhood = neighborhood_colors, 
             Response = response_colors,
             Sender = sender_colors,
             Receiver = receiver_colors),
  show_legend = TRUE
)


#plot_labels <- sub("\\s*\\(.*", "", plot_ids)

# Assuming 'combined_df_wide' is your data frame
# Create shortened column names


# remove NAs
combined_df_wide <- combined_df_wide[,!colnames(combined_df_wide) %like% c('%NA %')]
short_colnames <- sub("\\s*\\(.*", "", colnames(combined_df_wide))
# Create the matrix with shortened column names
mat <- as.matrix(combined_df_wide)
colnames(mat) <- short_colnames

anno_df_row <- data.frame(rownames(combined_df_wide))

library(tidyr)
anno_df_row <- anno_df_row %>% separate(`rownames.combined_df_wide.`, c("int", "pathway"), sep = " ", remove = F) %>%
  select(`rownames.combined_df_wide.`, pathway) %>%
  tibble::column_to_rownames("rownames.combined_df_wide.")

anno_df_row$pathway[grep("IL",anno_df_row$pathway)] = "IL"

# Create the column annotation
row_ha <- ComplexHeatmap::rowAnnotation(
  Pathway = anno_df_row$pathway,
  #col = list(Neighborhood = neighborhood_colors),
  col = list(Pathway = c(CCL = "#FFFF00", CXCL = "darkblue", IL = "#A6761D")),
  show_legend = TRUE
)


pdf('Rescaled_noMHC_COLLAGEN_fromDP_nh_contribution_CXCL.pdf', height = 20, width = 18)
# Now use this matrix in your Heatmap function

set.seed(100)
test = ComplexHeatmap::draw(ComplexHeatmap::Heatmap(mat,
             name = "Probability",
             #column_title = "Merged Column",
             row_title = "Interaction Name",
             right_annotation = row_ha,
             top_annotation = col_anno,
             show_row_names = TRUE,
             show_column_names = TRUE,
             column_names_rot = 90,
             clustering_distance_columns = "euclidean",
             clustering_method_columns = "ward.D",
             clustering_distance_rows = "euclidean",
             clustering_method_rows = "ward.D", 
             cluster_column_slices = T,
             column_names_max_height = unit(15, 'cm'), column_km = 7))
test
dev.off()
```
```{r Fig 4c-DotPlot of ligand (myeloid) and receptor (T cells) in tumor/immune/Tcell high NHs}
load("./CosMX_TMA/CosMX_RNA_merged.rda")

CosMX_RNA_merged <- CosMX_RNA_merged %>%
  Seurat::AddMetaData(
    metadata = case_when(
      CosMX_RNA_merged$k10_NhCoord20_anno == "Tumor_Immune_Mixed" ~ 'Tumor_Immune_Tcell_High',
      CosMX_RNA_merged$k10_NhCoord20_anno == "Macrophage_High" ~ "Immune_Macrophage_High",
      CosMX_RNA_merged$k10_NhCoord20_anno == "DC_T_iCAF_Tumor_Mixed" ~ "ap_iCAF_Immune_Mixed",
      CosMX_RNA_merged$k10_NhCoord20_anno == "CAF_Immune_Mixed" ~ "myCAF_Immune_Mixed",
      TRUE ~ as.character(CosMX_RNA_merged$k10_NhCoord20_anno)
    ), col.name = "k10_NhCoord20_anno_new"
  )

 unique(CosMX_RNA_merged$k10_NhCoord20_anno_new)
#[1] "Bcell_Plasma"             "Endothelial"              "Tumor_Immune_Tcell_High" 
#[4] "ap_iCAF_Immune_Mixed"     "Immune_Macrophage_High"   "myCAF_Immune_Mixed"      
#[7] "CAFs"                     "Tumor_High"               "Myeloid_K17+_Tumor_Mixed"
 
 myeloid_k17_tumor_mixed <- CosMX_RNA_merged[,CosMX_RNA_merged$k10_NhCoord20_anno_new == "Myeloid_K17_Tumor_Mixed"]
 
 p1 <- DotPlot(myeloid_k17_tumor_mixed[,grep('Mon|Mac|DC', myeloid_k17_tumor_mixed$annot_cluster2)], features = c('IL16', 'IL11', 'CCL19', 'CCL21'), col.min = 0, cols = 'RdBu', split.by = 'Response', group.by = 'annot_cluster2')

p2 <- DotPlot(myeloid_k17_tumor_mixed[,grep('CD4|CD8|Treg', myeloid_k17_tumor_mixed$annot_cluster2)], features = c('CCR7', 'CD4', 'IL11RA'), col.min = 0, cols = 'RdBu', split.by = 'Response', group.by = 'annot_cluster2')

pdf('myeloid_k17_tumor_mixed_NH_IL_CCL_dotplot_by_response.pdf', width = 12, height = 4)
cowplot::plot_grid(p1, p2)
dev.off()


p1 <- DotPlot(myeloid_k17_tumor_mixed[,grep('Mon|Mac|DC', myeloid_k17_tumor_mixed$annot_cluster2)], features = c('CXCL9', 'CXCL10', 'CXCL16'), col.min = 0, cols = 'RdBu', split.by = 'Response', group.by = 'annot_cluster2') 

p2 <- DotPlot(myeloid_k17_tumor_mixed[,grep('CD4|CD8|Treg', myeloid_k17_tumor_mixed$annot_cluster2)], features = c('CXCR3', 'CXCR6'), col.min = 0, cols = 'RdBu', split.by = 'Response', group.by = 'annot_cluster2') 

pdf('myeloid_k17_tumor_mixed_NH_CXCL_CCL_dotplot_by_response.pdf', width = 13, height = 4)
cowplot::plot_grid(p1, p2)
dev.off()

p1 <- DotPlot(myeloid_k17_tumor_mixed[,grep('Mon|Mac|DC', myeloid_k17_tumor_mixed$annot_cluster2)], features = c('IL1B', 'CCL4', 'CCL3', 'CCL13'), col.min = 0, cols = 'RdBu', split.by = 'Response', group.by = 'annot_cluster2')

p2 <- DotPlot(myeloid_k17_tumor_mixed[,grep('CD4|CD8|Treg', myeloid_k17_tumor_mixed$annot_cluster2)], features = c('IL1R1', 'IL1R2', 'CCR5', 'CCR1'), col.min = 0, cols = 'RdBu', split.by = 'Response', group.by = 'annot_cluster2')

pdf('myeloid_k17_tumor_mixed_NH_IL_CCL_dotplot_by_response.pdf', width = 12, height = 4)
cowplot::plot_grid(p1, p2)
dev.off()

immune_macrophage_high <- CosMX_RNA_merged[,CosMX_RNA_merged$k10_NhCoord20_anno_new == "Immune_Macrophage_High"]

p1 <- DotPlot(immune_macrophage_high[,grep('Mon|Mac|DC', immune_macrophage_high$annot_cluster2)], features = c('IL1B', 'CCL4', 'CCL3', 'CCL13'), col.min = 0, cols = 'RdBu', split.by = 'Response', group.by = 'annot_cluster2')

p2 <- DotPlot(immune_macrophage_high[,grep('CD4|CD8|Treg', immune_macrophage_high$annot_cluster2)], features = c('IL1R1', 'IL1R2', 'CCR5', 'CCR1'), col.min = 0, cols = 'RdBu', split.by = 'Response', group.by = 'annot_cluster2')

pdf('immune_macrophage_high_NH_IL_CCL_dotplot_by_response.pdf', width = 12, height = 4)
cowplot::plot_grid(p1, p2)
dev.off()

p1 <- DotPlot(immune_macrophage_high[,grep('Mon|Mac|DC', immune_macrophage_high$annot_cluster2)], features = c('CXCL9', 'CXCL10', 'CXCL16'), col.min = 0, cols = 'RdBu', split.by = 'Response', group.by = 'annot_cluster2') 

p2 <- DotPlot(immune_macrophage_high[,grep('CD4|CD8|Treg', immune_macrophage_high$annot_cluster2)], features = c('CXCR3', 'CXCR6'), col.min = 0, cols = 'RdBu', split.by = 'Response', group.by = 'annot_cluster2') 

pdf('immune_macrophage_high_NH_CXCL_CCL_dotplot_by_response.pdf', width = 13, height = 4)
cowplot::plot_grid(p1, p2)
dev.off()


p1 <- DotPlot(immune_macrophage_high[,grep('Mon|Mac|DC', immune_macrophage_high$annot_cluster2)], features = c('CXCL9', 'CXCL10', 'CXCL16', 'CCL5'), col.min = 0, cols = 'RdBu', split.by = 'Response', group.by = 'annot_cluster2')

p2 <- DotPlot(immune_macrophage_high[,grep('CD4|CD8|Treg', immune_macrophage_high$annot_cluster2)], features = c('CXCR3', 'CXCR6', 'CCR5'), col.min = 0, cols = 'RdBu', split.by = 'Response', group.by = 'annot_cluster2')

pdf('immune_macrophage_high_NH_CXCL_CCL_dotplot_by_response.pdf', width = 14, height = 4)
cowplot::plot_grid(p1, p2)
dev.off()
 

tumor_immune_tcell_high <- CosMX_RNA_merged[,CosMX_RNA_merged$k10_NhCoord20_anno_new == "Tumor_Immune_Tcell_High"]

p1 <- DotPlot(tumor_immune_tcell_high[,grep('Mon|Mac|DC', tumor_immune_tcell_high$annot_cluster2)], features = c('CXCL9', 'CXCL10', 'CXCL16'), col.min = 0, cols = 'RdBu', split.by = 'Response', group.by = 'annot_cluster2') 

p2 <- DotPlot(tumor_immune_tcell_high[,grep('CD4|CD8|Treg', tumor_immune_tcell_high$annot_cluster2)], features = c('CXCR3', 'CXCR6'), col.min = 0, cols = 'RdBu', split.by = 'Response', group.by = 'annot_cluster2') 

pdf('tumor_immune_tcell_high_NH_CXCL_CCL_dotplot_by_response.pdf', width = 13, height = 4)
cowplot::plot_grid(p1, p2)
dev.off()

p1 <- DotPlot(tumor_immune_tcell_high[,grep('Mon|Mac|DC', tumor_immune_tcell_high$annot_cluster2)], features = c('CXCL9', 'CXCL10', 'CXCL16', 'CCL5'), col.min = 0, cols = 'RdBu', split.by = 'Response', group.by = 'annot_cluster2')

p2 <- DotPlot(tumor_immune_tcell_high[,grep('CD4|CD8|Treg', tumor_immune_tcell_high$annot_cluster2)], features = c('CXCR3', 'CXCR6', 'CCR5'), col.min = 0, cols = 'RdBu', split.by = 'Response', group.by = 'annot_cluster2')

pdf('tumor_immune_tcell_high_NH_CXCL_CCL_dotplot_by_response.pdf', width = 14, height = 4)
cowplot::plot_grid(p1, p2)
dev.off()


p1 <- DotPlot(tumor_immune_tcell_high[,grep('Mon|Mac|DC', tumor_immune_tcell_high$annot_cluster2)], features = c('IL16', 'IL11', 'CCL19', 'CCL21'), col.min = 0, cols = 'RdBu', split.by = 'Response', group.by = 'annot_cluster2')

p2 <- DotPlot(tumor_immune_tcell_high[,grep('CD4|CD8|Treg', tumor_immune_tcell_high$annot_cluster2)], features = c('CCR7', 'CD4', 'IL11RA'), col.min = 0, cols = 'RdBu', split.by = 'Response', group.by = 'annot_cluster2')

pdf('tumor_immune_tcell_high_NH_IL_CCL_dotplot_by_response.pdf', width = 12, height = 4)
cowplot::plot_grid(p1, p2)
dev.off()
```

